JAGS Model

### 2020-02-19 Rcodes/JAGS_overdoses.Rmd
RJAGS output done

```{r message=FALSE, warning=FALSE}
# install packages
if (!require(runjags)) install.packages("runjags")
if (!require(rjags)) install.packages("rjags")
if (!require(coda)) install.packages("coda")

library('runjags')
library('rjags')
library('coda')
```
The data is the same data from pymc3 with Python.  
Todo: build a pipeline to connect the python (pymc3) and R (JAGS)

@@

            )
```
**Note: for the list object usually named 'data' or 'dat' in JAGS context, do not use arrow but use equal sign to define elements of the list.**
``` {r run the first model without error }
jags.simple <- jags.model(file='basic_model.txt',
                          data=dat)
```

>>>>

```{r message=FALSE, warning=FALSE}
# install packages
if (!require(rjags)) install.packages("rjags", dependencies = TRUE)
if (!require(coda)) install.packages("coda", dependencies = TRUE)
if (!require(tidyverse)) install.packages("tidyverse", dependencies = TRUE)
if (!require(tinytex)) install.packages("tinytex", dependencies = TRUE)

library('rjags')
library('coda')
library('tidyverse')
library('tinytex')

```
The data is the same data from pymc3 with Python.  
Todo: build a pipeline to connect the python (pymc3) and R (JAGS)

@@

            )
```
**Note: for the list object usually named 'data' or 'dat' in JAGS context, do not use arrow but use equal sign to define elements of the list.**
``` {r run the first model without error }
interations = 1000
burnin= floor(interations/2)
chains=2
# inits = list()
simple.model <- jags.model(file='basic_model.txt',
                          data=dat,
                          n.chains = chains)
simple.model
```

### O_t

```{r}
params= c('o_t')
samples <- coda.samples(simple.model, params, n.iter = 1000)
```

# Q1: is init necessary? and it's a characteristic of Gibbs sampling?

```{r }
summary(window(samples), start=burnin)
```

```{r include=FALSE}
plot(samples)
```

### Boxplots of O_t

# q2: I see two elements from the samples list. Which one I should use it or should I use both?

```{r yield a data frame}
temp = as.matrix(samples)
colnames(temp) <- seq(1,12)
head(temp)
df_o_t <- as.data.frame(temp)
head(df_o_t)
```

```{r tidy the data frame}
df_o_t <- gather(df_o_t, key = 'month',value = 'o_t')
df_o_t$month <- factor(df_o_t$month,levels = seq(1,12))
str(df_o_t)
```

```{r}
o_t_values=data.frame('month'=seq(1,12),'o_t'=df$o_t)
o_t_values$month <- factor(o_t_values$month,levels = seq(1,12))

ggplot()+geom_point(aes(x=o_t_values$month, y=o_t_values$o_t),color='red')+geom_boxplot(aes(x=month,y=o_t),data = df_o_t)
```

```{r}
params= c('u_t','x_a')
ppc <- coda.samples(simple.model, params, n.iter = 1000)
```

```{r}
summary(window(ppc),start=burnin)

```

```{r eval=FALSE, include=FALSE}
plot(ppc)
```

```{r}
temp = as.matrix(ppc)

df_u_t=temp[,1:12]
df_x_a=temp[,13:24]

test <- as.matrix(df_u_t)
colnames(test) <- seq(1,12)
head(test)
mtx_u_t <- as.data.frame(test)
head(mtx_u_t)

df_u_t <- gather(mtx_u_t, key = 'month',value = 'u_t')
head(df_u_t)

df_u_t$month <- factor(df_u_t$month,levels = seq(1,12))
str(df_u_t)

u_t_values=data.frame('month'=seq(1,12),'u_t'=df$u_t)
u_t_values$month <- factor(u_t_values$month,levels = seq(1,12))

ggplot()+geom_point(aes(x=u_t_values$month, y=u_t_values$u_t),color='red')+geom_boxplot(aes(x=month,y=u_t),data = df_u_t)
```

```{r}

temp = as.matrix(ppc)
df_x_a=temp[,13:24]

test <- as.matrix(df_x_a)
colnames(test) <- seq(1,12)
head(test)
mtx_x_a <- as.data.frame(test)
head(mtx_x_a)

df_x_a <- gather(mtx_x_a, key = 'month',value = 'x_a')
head(df_x_a)

df_x_a$month <- factor(df_x_a$month,levels = seq(1,12))
str(df_x_a)

x_a_values=data.frame('month'=seq(1,12),'x_a'=df$x_a)
x_a_values$month <- factor(x_a_values$month,levels = seq(1,12))

ggplot()+geom_point(aes(x=x_a_values$month, y=x_a_values$x_a),color='red')+geom_boxplot(aes(x=month,y=x_a),data = df_x_a)
```
